---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# advent2020

<!-- badges: start -->
<!-- badges: end -->

The goal of advent2020 is to document my Advent of Code 2020 solutions.

## Installation

You can install the released version of advent2020 from [Github](http://github.com/) with:

``` r
devtools::install_github('lashlee/advent2020')
```

## Setup

It will make your life easier using `get_data` to copy your Advent of Code session cookie to an environment variable named `AOC_SC`. Here is how to access your cookie: https://developers.google.com/web/tools/chrome-devtools/storage/cookies.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(advent2020)
## basic example code
## TODO
```

## Solutions

* [Day 1](https://github.com/lashlee/advent2020/blob/master/inst/solutions/day1.md)
